---
title: "modreport"
format: 
  html:
    toc: true
    toc-depth: 4
knitr:
  opts_chunk: 
    collapse: true
    comment: "" 

execute:
  echo: false

vignette: >
  %\VignetteIndexEntry{modreport}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| echo: true
library(modreport)
library(lobstr)
```

```{r}
fs::dir_tree("../R")
```


## App structure

The standalone app file (`launch_app()`) calls the `app_ui()` and `app_server()`:

```{r}
#| label: full-app
lobstr::ast(
  launch_app(
    app_ui(),
    app_server()
  )
)
```

## Modules 

The module files: 

1. `R/mod_input.R`: collects user inputs        
2. `R/mod_download_report.R`: downloads report from .Rmd template       
3. `R/mod_graph_output.R`: `ggplot2` graph outputs   
4. `R/mod_table_output.R`: table output      


```{r}
lobstr::ast(
  launch_app(
    app_ui(
      mod_input_ui(),
      mod_download_report_ui(),
      mod_graph_output_ui(),
      mod_table_output_ui()
    ),
    app_server(
      mod_input_server(),
      mod_download_report_server(),
      mod_graph_output_server(),
      mod_table_output_server()
    )
  )
)
```

## Utility functions

The utility functions:

1. `R/create_report_template_content.R`: returns the template as a string      
2. `R/create_report_template.R`: generates the R Markdown template programmatically     
3. `R/create_error_report.R`: generates a user-friendly error page if the report fails

```{r}
lobstr::ast(
  launch_app(
    create_report_template_content(),
    app_ui(
      mod_input_ui(),
      mod_download_report_ui(),
      mod_graph_output_ui(),
      mod_table_output_ui()
    ),
    app_server(
      mod_input_server(),
      mod_download_report_server(
        create_report_template(),
        create_error_report()
      ),
      mod_graph_output_server(),
      mod_table_output_server()
    )
  )
)
```
